Modeling and Simulation of Online Reprocessing in the Thorium-Fueled Molten Salt Breeder Reactor

### 2018-09-11 highlights/highlights.tex
highlights grammar

\begin{document}
\begin{frontmatter}
\title{Modeling and Simulation of Online Reprocessing in the Thorium-Fuelled Molten Salt Breeder Reactor}
\end{frontmatter}
\section*{Highlights}
\begin{itemize}
       \item Highlight 1
       \item Highlight 2
       \item Highlight 3
\end{itemize}
\end{document}

>>>>

\begin{document}
\begin{frontmatter}
\title{Modeling and Simulation of Online Reprocessing in the Thorium-Fueled Molten Salt Breeder Reactor}
\end{frontmatter}
\section*{Highlights}
\begin{itemize}
       \item A python script, SaltProc, is coupled with SERPENT to simulate 
               material feeds and removals during depletion in MSBR.
       \item Ten years of depletion and fuel processing in a thorium-fueled 
               MSBR is simulated to find the equilibrium fuel composition.
       \item Effects of the fuel salt irradiation with online reprocessing on 
               MSBR operations are identified.
       \item Benefits of online fission product removal in the thermal 
               spectrum MSBR are identified.
\end{itemize}
\end{document}
